Modern Graph Generators: A Survey

### 2018-09-13 generators_community_detection.tex
Minor corrections

Community detection is one of the many graph analytics algorithms typically used on domains such as social networks or bioinformatics. Communities are groups of vertices that are highly connected among them, while being scarcely connected to the rest of the graph. Such communities emerge from the fact that real graphs are not random, but follow real-world dynamics that make similar entities to have a larger probability to be connected. As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks. Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies. In order to compare the quality of the different proposed techniques, one needs graphs with reference communities, that is, communities known beforehand. Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.

The first attempts to compare community detection algorithms using synthetic graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi subgraphs, connected more internally than externally~\cite{danon2005comparing}. Each of these subgraphs has the same size and the same internal/external density of edges. However, such graphs miss the realism observed in real graphs, where communities are of different sizes and densities. Thus, Lancichinetti, Fortunato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark graphs for community detection where communities are of different sizes and densities. The generator generates communities of different sizes following a power-law distribution whose parameters can be configured. The degree of the nodes is also sampled from a power-law distribution. Additionally, the generator introduces the concept of the ``mixing factor'', which specifies the fraction of its links connecting nodes belonging to different communities. Such parameter allows to tune the degree of modularity of the generated graph, thus testing the robustness of the algorithms under different conditions. The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints. Lancichinetti, Fortunato and Radicchi \cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities. Overlapping communities extend the notion of communities by allowing the sharing of vertices, thus a vertex can belong to more than one community. This extended generator allows controlling the same parameters of the previous version, but also the amount of overlap of the generated communities.

Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining} proposed hte use of real graphs with explicit group annotations (e.g. forums in a social network, categories of products, etc.) to infer what they call ``meta-communities'', and use them to evaluate overlapping community detection algorithms. However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities --the authors refer to them as structural communities-- and meta-communities.  This result reveals that those algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.

@@

The differences observed between structural and meta-communities reveal the need of more accurate community defeinitions thight more specifically to the domain or use case. Current community detection algorithms and graph generators for community detection are stuck to the traditional (and vague) definition of community, assuming that there exists a single algorithm that would fit all the use cases. Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resemble that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.revealing which are the best algorithms for each particular scenario.

>>>>

Community detection is one of the many graph analytics algorithms typically used on domains such as social networks or bioinformatics. Communities are groups of vertices that are highly connected among them, while being scarcely connected to the rest of the graph. Such communities emerge from the fact that real graphs are not random, but follow real-world dynamics that make similar entities to have a larger probability to be connected. As a consequence, detected communities are used to reveal vertices with similar characteristics, for instance to discover functionally equivalent proteins in protein-protein interaction networks, or persons with similar interests in social networks. Such applications have made community detection a hot topic during the last fifteen years with tens of developed algorithms and detection strategies.\TODO{references} In order to compare the quality of the different proposed techniques, one needs graphs with \emph{reference communities}, that is, communities known beforehand. Since it is very difficult to have large real graphs with reference communities (mainly because these would require a manual labeling), graphs for benchmarking community detection algorithms are typically generated synthetically.

The first attempts to compare community detection algorithms using synthetic graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi subgraphs, connected more internally than externally~\cite{danon2005comparing}. Each of these subgraphs has the same size and the same internal/external density of edges. However, such graphs miss the realism observed in real graphs, where communities are of different sizes and densities. Thus, Lancichinetti, Fortunato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark graphs for community detection where communities are of different sizes and densities. The generator generates communities of different sizes following a power-law distribution whose parameters can be configured. The degree of the nodes is also sampled from a power-law distribution. Additionally, the generator introduces the concept of the ``mixing factor'', which specifies the fraction of its links connecting nodes belonging to different communities. Such parameter allows to tune the degree of modularity of the generated graph, thus testing the robustness of the algorithms under different conditions. The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints. Lancichinetti, Fortunato and Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities. Overlapping communities extend the notion of communities by allowing the sharing of vertices, thus a vertex can belong to more than one community. This extended generator allows controlling the same parameters of the previous version, but also the amount of overlap of the generated communities.

Besides synthetic graph generators, Yang and Leskovec~\cite{yang2015defining} proposed the use of real-world graphs with explicit group annotations (e.g., forums in a social network, categories of products, etc.) to infer what they call ``meta-communities'', and use them to evaluate overlapping community detection algorithms. However, a recent study from Hric, Darst and Fortunato~\cite{hric2014community} reveal a loose correspondence between  communities (the authors refer to them as structural communities) and meta-communities.  This result reveals that  algorithms working for structural communities do not work well for finding meta-communities and viceversa, suggesting significantly different underlying characteristics between the two types of communities, which are yet to be identified.

@@

The differences observed between structural and meta-communities reveal the need of more accurate community definitions tight more specifically to the domain or use case. Current community detection algorithms and graph generators for community detection are stuck to the traditional (and vague) definition of community, assuming that there exists a single algorithm that would fit all the use cases. Thus, future work requires the study of domain-specific community characteristics that can be used to generate graphs with a community structure that accurately resemble that of specific use cases, and thus revealing which are the best algorithms for each particular scenario.

### 2018-09-13 generators_streaming.tex
Minor corrections

\subsubsection{Graph Data Streaming}
\label{sec:generators_streaming}
One way for dealing with big graph is to process them using the \emph{streaming} mode where the data stream could consist of the edges of the graph. In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount memory~\cite{mcgregor2014graph}. The streaming mode has attracted the attention of the RDF and Semantic Web community. Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines. The framework uses a data generator for Stream Social network data Generator (\texttt{S2Gen}) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information. The data generator of this framework provides the users the flexibility to control the characteristics of the generated data by tanning a range of parameters including the period in which the social activities are generated (generating period), the maximum number of posts/comments/photos for each user per week and the correlation probabilities between the different objects (e.g., users) in the social network.

Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, \texttt{RSPLab}. The \texttt{Streamer} component of this framework is designed to publishe RDF streams from the various existing RDF benchmarks (e.g., BSBM, LUBM) (See Section~\ref{sec:generators_LinkedData}). In particular, the \texttt{Streamer}  component uses \texttt{TripleWave}, an open-source framework for publishing
and sharing RDF streams on the Web~\cite{mauri2016triplewave}.   \texttt{TripleWave}\footnote{\url{http://streamreasoning.github.io/TripleWave/}} acts as a mean for plugging in diverse Web data sources and for consuming streams in both push and pull mode.

>>>>

\subsubsection{Graph Data Streaming}
\label{sec:generators_streaming}
One way for dealing with big graphs is to process them using the \emph{streaming} mode where the data stream could consist of the edges of the graph. In this mode, the graph processing algorithms can process the input stream in the order it arrives while using only a limited amount memory~\cite{mcgregor2014graph}. The streaming mode has mainly  attracted the attention of the RDF and Semantic Web community. Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines. The framework uses a data generator for Stream Social network data Generator (S2Gen) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information. The data generator of this framework provides the users the flexibility to control the characteristics of the generated data by tanning a range of parameters including the period in which the social activities are generated (generating period), the maximum number of posts/comments/photos for each user per week and the correlation probabilities between the different objects (e.g., users) in the social network.

Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, RSPLab. The Streamer component of this framework is designed to publish RDF streams from the various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}). In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an open-source framework for publishing and sharing RDF streams on the Web~\cite{mauri2016triplewave}.   TripleWave acts as a mean for plugging in diverse Web data sources and for consuming streams in both push and pull mode.
